---
title: "Dissertation_RMD file"
author: "B247721"
date: "2024-06-24"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())

library(tidyverse)
library(brms)
library(broom.mixed)
library(posterior)
library(knitr)
library(ggplot2)
library(tidybayes)
library(stats)
library(lmtest)
library(ggdist)
library(bayesmeta)
library(bayesplot)
library(metafor)
library(marginaleffects)
library(dplyr)
library(forcats)
library(stringr)
library(purrr)
library(glue)

seed <- 999
```

## Read data for age at onset studies

```{r read-data}
retrospective_2 <- read_csv("data/retrospective.csv") %>% 
  mutate(
    SE = SD / sqrt(N),
    mobi = factor(group, levels = c("monolingual", "bilingual"))
  )

```

## Set the Prior
```{r}
meta_analysismodel_1_priors <- c(
  prior(lkj(2), class = cor),
  prior(student_t(3, 0, 9), class = sd),
  prior(normal(65, 22.5), class = b)
)
```


##Fit the model with the group-level intercept "Study"
```{r}
meta_analysismodel_1 <- brm(
  mean | se(SE) ~ 0 + mobi + (0 + mobi | Study),
  data = retrospective_2,
  prior = meta_analysismodel_1_priors,
  cores = 4,
  file = "data/cache/meta_analysismodel_1",
  seed = seed
)
summary(meta_analysismodel_1)

```
```{r}
plot(meta_analysismodel_1, ask = FALSE)
```


```{r}
avg_comparisons(meta_analysismodel_1, variables = "mobi")
```



```{r}

spread_draws(meta_analysismodel_1, r_Study[study,mobi]) %>% 
  ggplot(aes(r_Study, reorder(as.factor(study), r_Study, mean))) +
  stat_halfeye() +
  facet_grid(~mobi)


```



```{r}
# Check the variable names in the model draws
model_draws <- as_draws_df(meta_analysismodel_1)
names(model_draws)

```
#Forest plot for the main Meta-analysis
```{r}

# Extract draws using the correct variable names
draws <- spread_draws(meta_analysismodel_1, 
                      b_mobimonolingual, 
                      b_mobibilingual, 
                      `r_Study[Alladi.et.al.2013,mobimonolingual]`, 
                      `r_Study[Alladi.et.al.2017,mobimonolingual]`,
                      `r_Study[Berkes.et.al.2020,mobimonolingual]`,
                      `r_Study[Bialystok.et.al.2007,mobimonolingual]`,
                      `r_Study[Bialystok.et.al.2014,mobimonolingual]`,
                      `r_Study[Chertkow.et.al.2010,mobimonolingual]`,
                      `r_Study[Clare.et.al.2016,mobimonolingual]`,
                      `r_Study[Craik.et.al.2010,mobimonolingual]`,
                      `r_Study[de.Leon.et.al.2020,mobimonolingual]`,
                      `r_Study[de.Leon.et.al.2024,mobimonolingual]`,
                      `r_Study[Duncan.et.al.2018,mobimonolingual]`,
                      `r_Study[Kowoll.et.al.2016,mobimonolingual]`,
                      `r_Study[Mendez..Chavez.&.Akhlaghipour.2020,mobimonolingual]`,
                      `r_Study[Ossher.et.al.2013,mobimonolingual]`,
                      `r_Study[Perani.et.al.2017,mobimonolingual]`,
                      `r_Study[Ramakrishnan.et.al.2017,mobimonolingual]`,
                      `r_Study[Woumans.et.al.2015,mobimonolingual]`,
                      `r_Study[Zheng.et.al.2018,mobimonolingual]`,
                      `r_Study[Alladi.et.al.2013,mobibilingual]`, 
                      `r_Study[Alladi.et.al.2017,mobibilingual]`,
                      `r_Study[Berkes.et.al.2020,mobibilingual]`,
                      `r_Study[Bialystok.et.al.2007,mobibilingual]`,
                      `r_Study[Bialystok.et.al.2014,mobibilingual]`,
                      `r_Study[Chertkow.et.al.2010,mobibilingual]`,
                      `r_Study[Clare.et.al.2016,mobibilingual]`,
                      `r_Study[Craik.et.al.2010,mobibilingual]`,
                      `r_Study[de.Leon.et.al.2020,mobibilingual]`,
                      `r_Study[de.Leon.et.al.2024,mobibilingual]`,
                      `r_Study[Duncan.et.al.2018,mobibilingual]`,
                      `r_Study[Kowoll.et.al.2016,mobibilingual]`,
                      `r_Study[Mendez..Chavez.&.Akhlaghipour.2020,mobibilingual]`,
                      `r_Study[Ossher.et.al.2013,mobibilingual]`,
                      `r_Study[Perani.et.al.2017,mobibilingual]`,
                      `r_Study[Ramakrishnan.et.al.2017,mobibilingual]`,
                      `r_Study[Woumans.et.al.2015,mobibilingual]`,
                      `r_Study[Zheng.et.al.2018,mobibilingual]`)


draws_long <- draws %>%
  pivot_longer(
    cols = starts_with("r_Study"),
    names_to = c("Study", "Group"),
    names_pattern = "r_Study\\[(.*),(.*)\\]"
  )

# Calculate study-specific effects and differences
draws_diff <- draws_long %>%
  pivot_wider(names_from = Group, values_from = value) %>%
  mutate(
    study_effect_mono = mobimonolingual + b_mobimonolingual,
    study_effect_bi = mobibilingual + b_mobibilingual,
    difference = study_effect_bi - study_effect_mono
  ) %>%
  select(Study, .draw, difference)

# Summarize the differences for each study
draws_summary <- draws_diff %>%
  group_by(Study) %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  ungroup()

# Add an summary effect row
overall_effect <- draws_diff %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  mutate(Study = "Summary_effect")

draws_summary <- bind_rows(draws_summary, overall_effect)

# Generate the forest plot
ggplot(draws_summary, aes(x = mean_diff, y = fct_reorder(Study, mean_diff))) +
  geom_vline(xintercept = 0, size = .25, lty = 2) +  # Vertical line at zero
  geom_pointrange(aes(xmin = lower, xmax = upper), size = .5) +  # Plot credible intervals
  geom_point(size = 3, color = "dodgerblue") +  # Plot mean differences
  geom_text(
    aes(label = glue("{round(mean_diff, 2)} [{round(lower, 2)}, {round(upper, 2)}]"), x = max(upper) + 0.5), 
    hjust = 0
  ) + 
  labs(
    title = "Forest Plot of Meta-analytic Effects",
    x = "Difference in Age at Onset",
    y = "Study"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) + 
  coord_cartesian(clip = "off", xlim = c(-4, 16))
```


## Draw funnel plot
```{r}
# Extract draws using the correct variable names
draws <- spread_draws(meta_analysismodel_1, 
                      b_mobimonolingual, 
                      b_mobibilingual, 
                      `r_Study[Alladi.et.al.2013,mobimonolingual]`, 
                      `r_Study[Alladi.et.al.2017,mobimonolingual]`,
                      `r_Study[Berkes.et.al.2020,mobimonolingual]`,
                      `r_Study[Bialystok.et.al.2007,mobimonolingual]`,
                      `r_Study[Bialystok.et.al.2014,mobimonolingual]`,
                      `r_Study[Chertkow.et.al.2010,mobimonolingual]`,
                      `r_Study[Clare.et.al.2016,mobimonolingual]`,
                      `r_Study[Craik.et.al.2010,mobimonolingual]`,
                      `r_Study[de.Leon.et.al.2020,mobimonolingual]`,
                      `r_Study[de.Leon.et.al.2024,mobimonolingual]`,
                      `r_Study[Duncan.et.al.2018,mobimonolingual]`,
                      `r_Study[Kowoll.et.al.2016,mobimonolingual]`,
                      `r_Study[Mendez..Chavez.&.Akhlaghipour.2020,mobimonolingual]`,
                      `r_Study[Ossher.et.al.2013,mobimonolingual]`,
                      `r_Study[Perani.et.al.2017,mobimonolingual]`,
                      `r_Study[Ramakrishnan.et.al.2017,mobimonolingual]`,
                      `r_Study[Woumans.et.al.2015,mobimonolingual]`,
                      `r_Study[Zheng.et.al.2018,mobimonolingual]`,
                      `r_Study[Alladi.et.al.2013,mobibilingual]`, 
                      `r_Study[Alladi.et.al.2017,mobibilingual]`,
                      `r_Study[Berkes.et.al.2020,mobibilingual]`,
                      `r_Study[Bialystok.et.al.2007,mobibilingual]`,
                      `r_Study[Bialystok.et.al.2014,mobibilingual]`,
                      `r_Study[Chertkow.et.al.2010,mobibilingual]`,
                      `r_Study[Clare.et.al.2016,mobibilingual]`,
                      `r_Study[Craik.et.al.2010,mobibilingual]`,
                      `r_Study[de.Leon.et.al.2020,mobibilingual]`,
                      `r_Study[de.Leon.et.al.2024,mobibilingual]`,
                      `r_Study[Duncan.et.al.2018,mobibilingual]`,
                      `r_Study[Kowoll.et.al.2016,mobibilingual]`,
                      `r_Study[Mendez..Chavez.&.Akhlaghipour.2020,mobibilingual]`,
                      `r_Study[Ossher.et.al.2013,mobibilingual]`,
                      `r_Study[Perani.et.al.2017,mobibilingual]`,
                      `r_Study[Ramakrishnan.et.al.2017,mobibilingual]`,
                      `r_Study[Woumans.et.al.2015,mobibilingual]`,
                      `r_Study[Zheng.et.al.2018,mobibilingual]`)

# Reshape data to long format for easier handling
draws_long <- draws %>%
  pivot_longer(
    cols = starts_with("r_Study"),
    names_to = c("Study", "Group"),
    names_pattern = "r_Study\\[(.*),(.*)\\]"
  )

# Calculate study-specific effects and differences
draws_diff <- draws_long %>%
  pivot_wider(names_from = Group, values_from = value) %>%
  mutate(
    study_effect_mono = mobimonolingual + b_mobimonolingual,
    study_effect_bi = mobibilingual + b_mobibilingual,
    difference = study_effect_bi - study_effect_mono
  ) %>%
  select(Study, .draw, difference)

# Summarize the differences for each study
draws_summary <- draws_diff %>%
  group_by(Study) %>%
  summarise(
    mean_diff = mean(difference),
    # lower = quantile(difference, 0.025),
    # upper = quantile(difference, 0.975)
    se_diff = sd(difference)
  ) %>%
  ungroup()

# Add an overall effect row
ovearall_draws <- as_draws_df(meta_analysismodel_1) %>% 
  mutate(difference = b_mobibilingual - b_mobimonolingual)

overall_effect <- ovearall_draws %>%
  summarise(
    mean_diff = mean(difference),
    se_diff = sd(difference),
    lower = mean_diff - (1.96 * se_diff),
    upper = mean_diff + (1.96 * se_diff)
  ) %>%
  mutate(Study = "Overall")

draws_summary <- bind_rows(draws_summary, overall_effect)


# Function to create and save funnel plots
create_funnel_plot <- function(estimates_data, meta_ln_bm_est, meta_ln_bm_q2.5, meta_ln_bm_q97.5, filename) {
  # Compute the range of standard errors
  e.max <- max(estimates_data$se_diff)
  se_range <- seq(0, e.max, by = 0.001)
  
  # Create a tibble for confidence interval boundaries
  ci <- tibble(
    x_seq = se_range,
    ci_lo = meta_ln_bm_est - 1.96 * se_range,
    ci_up = meta_ln_bm_est + 1.96 * se_range
  )
  
  # Create the funnel plot
  funnel_plot <- estimates_data %>%
    ggplot(aes(mean_diff, se_diff)) +
    geom_line(aes(y = x_seq, x = ci_up), data = ci) +
    geom_line(aes(y = x_seq, x = ci_lo), data = ci) +
    geom_vline(aes(xintercept = 0), colour = "grey") +
    geom_vline(aes(xintercept = meta_ln_bm_est)) +
    annotate("rect", ymin = -Inf, ymax = Inf, xmin = meta_ln_bm_q2.5, xmax = meta_ln_bm_q97.5, alpha = 0.5, fill = "#a6cee3") +
    geom_point(size = 3) +
    labs(
      caption = "The shaded area is the 95% CI of the meta-analytical posterior,\nwhile the vertical line is the meta-analytical mean difference.",
      x = "Mean Estimate Difference"
    ) +
    scale_y_reverse()
  
  # Save the plot
  ggsave(filename, plot = funnel_plot, width = 7, height = 4.5)
}


# Create and save the funnel plot for the differences
create_funnel_plot(draws_summary, overall_effect$mean_diff, overall_effect$lower, overall_effect$upper, "./img/funnel-sd-diff2.png")

```

##Confounding variable: Education
```{r}
meta_analysismodel_2 <- brm(
  mean | se(SE) ~ 0 + mobi + years_of_education + (0 + mobi | Study),
  data = retrospective_2,
  prior = meta_analysismodel_1_priors,
  cores = 4,
  file = "data/cache/meta_analysismodel_2",
  seed = seed
)
summary(meta_analysismodel_2)
```

```{r}
avg_comparisons(meta_analysismodel_2, variables = "mobi")
```


##Sub-group analysis
#AD
```{r}
AD <- read.csv("data/AD.csv") %>% mutate(
    SE = SD / sqrt(N),
    mobi = factor(group, levels = c("monolingual", "bilingual"))
  )

```

```{r}
meta_analysismodel_3 <- brm(
  mean | se(SE) ~ 0 + mobi + (0 + mobi | Study),
  data = AD,
  prior = meta_analysismodel_1_priors,
  cores = 4,
  file = "data/cache/meta_analysismodel_3",
  seed = seed
)
summary(meta_analysismodel_3)
```
```{r}
avg_comparisons(meta_analysismodel_3, variables = "mobi")
```

```{r}
model_draws <- as_draws_df(meta_analysismodel_3)
names(model_draws)
```


#Forest plot for AD sub-group
```{r}
# Extract draws using the correct variable names
draws <- spread_draws(meta_analysismodel_3, 
                      b_mobimonolingual, 
                      b_mobibilingual, 
                      `r_Study[Alladi.et.al.2013,mobimonolingual]`, 
                      `r_Study[Berkes.et.al.2020,mobimonolingual]`,
                      `r_Study[Bialystok.et.al.2007,mobimonolingual]`,
                      `r_Study[Bialystok.et.al.2014,mobimonolingual]`,
                      `r_Study[Chertkow.et.al.2010,mobimonolingual]`,
                      `r_Study[Clare.et.al.2016,mobimonolingual]`,
                      `r_Study[Craik.et.al.2010,mobimonolingual]`,
                      `r_Study[de.Leon.et.al.2020,mobimonolingual]`,
                      `r_Study[Duncan.et.al.2018,mobimonolingual]`,
                      `r_Study[Kowoll.et.al.2016,mobimonolingual]`,
                      `r_Study[Mendez..Chavez.&.Akhlaghipour.2020,mobimonolingual]`,
                      `r_Study[Woumans.et.al.2015,mobimonolingual]`,
                      `r_Study[Zheng.et.al.2018,mobimonolingual]`,
                      `r_Study[Alladi.et.al.2013,mobibilingual]`, 
                      `r_Study[Berkes.et.al.2020,mobibilingual]`,
                      `r_Study[Bialystok.et.al.2007,mobibilingual]`,
                      `r_Study[Bialystok.et.al.2014,mobibilingual]`,
                      `r_Study[Chertkow.et.al.2010,mobibilingual]`,
                      `r_Study[Clare.et.al.2016,mobibilingual]`,
                      `r_Study[Craik.et.al.2010,mobibilingual]`,
                      `r_Study[de.Leon.et.al.2020,mobibilingual]`,
                      `r_Study[Duncan.et.al.2018,mobibilingual]`,
                      `r_Study[Kowoll.et.al.2016,mobibilingual]`,
                      `r_Study[Mendez..Chavez.&.Akhlaghipour.2020,mobibilingual]`,
                      `r_Study[Woumans.et.al.2015,mobibilingual]`,
                      `r_Study[Zheng.et.al.2018,mobibilingual]`)

# Reshape data to long format for easier handling
draws_long <- draws %>%
  pivot_longer(
    cols = starts_with("r_Study"),
    names_to = c("Study", "Group"),
    names_pattern = "r_Study\\[(.*),(.*)\\]"
  )

# Calculate study-specific effects and differences
draws_diff <- draws_long %>%
  pivot_wider(names_from = Group, values_from = value) %>%
  mutate(
    study_effect_mono = mobimonolingual + b_mobimonolingual,
    study_effect_bi = mobibilingual + b_mobibilingual,
    difference = study_effect_bi - study_effect_mono
  ) %>%
  select(Study, .draw, difference)

# Summarize the differences for each study
draws_summary <- draws_diff %>%
  group_by(Study) %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  ungroup()

# Add an overall effect row
overall_effect <- draws_diff %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  mutate(Study = "Summary_effect")

draws_summary <- bind_rows(draws_summary, overall_effect)

# Generate the forest plot
ggplot(draws_summary, aes(x = mean_diff, y = fct_reorder(Study, mean_diff))) +
  geom_vline(xintercept = 0, size = .25, lty = 2) +  # Vertical line at zero
  geom_pointrange(aes(xmin = lower, xmax = upper), size = .5) +  # Plot credible intervals
  geom_point(size = 3, color = "dodgerblue") +  # Plot mean differences
  geom_text(
    aes(label = glue("{round(mean_diff, 2)} [{round(lower, 2)}, {round(upper, 2)}]"), x = max(upper) + 0.5), 
    hjust = 0
  ) +  # Add text labels for each study
  labs(
    title = "Forest Plot of Meta-analytic Effect in AD Sub-group ",
    x = "Difference in Age at Onset",
    y = "Study"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) + # Adjust text size if needed
  coord_cartesian(clip = "off", xlim = c(-4, 16))
```


#FTD
```{r}
FTD <- read.csv("data/FTD.csv") %>% mutate(
    SE = SD / sqrt(N),
    mobi = factor(group, levels = c("monolingual", "bilingual"))
  )
```

```{r}
meta_analysismodel_4 <- brm(
  mean | se(SE) ~ 0 + mobi + (0 + mobi | Study),
  data = FTD,
  prior = meta_analysismodel_1_priors,
  cores = 4,
  file = "data/cache/meta_analysismodel_4",
  seed = seed
)
summary(meta_analysismodel_4)
```

#Forest plot for FTD sub-group
```{r}
model_draws1 <- as_draws_df(meta_analysismodel_4)
names(model_draws1)

# Extract draws using the correct variable names
draws <- spread_draws(meta_analysismodel_4, 
                      b_mobimonolingual, 
                      b_mobibilingual, 
                      `r_Study[.de.Leon.et.al.2024,mobimonolingual]`, 
                      `r_Study[Alladi.et.al.2013,mobimonolingual]`,
                      `r_Study[Alladi.et.al.2017,mobimonolingual]`,
                      `r_Study[de.Leon.et.al.2024,mobimonolingual]`,
                      `r_Study[.de.Leon.et.al.2024,mobibilingual]`,   
                      `r_Study[Alladi.et.al.2013,mobibilingual]`,    
                      `r_Study[Alladi.et.al.2017,mobibilingual]`,     
                      `r_Study[de.Leon.et.al.2024,mobibilingual]`)


draws_long <- draws %>%
  pivot_longer(
    cols = starts_with("r_Study"),
    names_to = c("Study", "Group"),
    names_pattern = "r_Study\\[(.*),(.*)\\]"
  )

# Calculate study-specific effects and differences
draws_diff <- draws_long %>%
  pivot_wider(names_from = Group, values_from = value) %>%
  mutate(
    study_effect_mono = mobimonolingual + b_mobimonolingual,
    study_effect_bi = mobibilingual + b_mobibilingual,
    difference = study_effect_bi - study_effect_mono
  ) %>%
  select(Study, .draw, difference)

# Summarize the differences for each study
draws_summary <- draws_diff %>%
  group_by(Study) %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  ungroup()

# Add an summary effect row
overall_effect <- draws_diff %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  mutate(Study = "Summary_effect")

draws_summary <- bind_rows(draws_summary, overall_effect)

# Generate the forest plot
ggplot(draws_summary, aes(x = mean_diff, y = fct_reorder(Study, mean_diff))) +
  geom_vline(xintercept = 0, size = .25, lty = 2) +  # Vertical line at zero
  geom_pointrange(aes(xmin = lower, xmax = upper), size = .5) +  # Plot credible intervals
  geom_point(size = 3, color = "dodgerblue") +  # Plot mean differences
  geom_text(
    aes(label = glue("{round(mean_diff, 2)} [{round(lower, 2)}, {round(upper, 2)}]"), x = max(upper) + 0.5), 
    hjust = 0
  ) + 
  labs(
    title = "Forest Plot of Meta-analytic Effect in FTD Sub-group ",
    x = "Difference in Age at Onset",
    y = "Study"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) + 
  coord_cartesian(clip = "off", xlim = c(-4, 18))
```


```{r}
avg_comparisons(meta_analysismodel_4, variables = "mobi")
```


#MCI
```{r}
MCI <- read.csv("data/MCI.csv") %>% mutate(
    SE = SD / sqrt(N),
    mobi = factor(group, levels = c("monolingual", "bilingual"))
  )
```

```{r}
meta_analysismodel_5 <- brm(
  mean | se(SE) ~ 0 + mobi + (0 + mobi | Study),
  data = MCI,
  prior = meta_analysismodel_1_priors,
  cores = 4,
  file = "data/cache/meta_analysismodel_5",
  seed = seed
)
summary(meta_analysismodel_5)
```

#Forest plot for MCI sub-group
```{r}
model_draws2 <- as_draws_df(meta_analysismodel_5)
names(model_draws2)

# Extract draws using the correct variable names
draws <- spread_draws(meta_analysismodel_5, 
                      b_mobimonolingual, 
                      b_mobibilingual, 
                      `r_Study[Berkes.et.al.2020,mobimonolingual]`,
                      `r_Study[Ossher.et.al.2013,mobimonolingual]`, 
                      `r_Study[Ramakrishnan.et.al.2017,mobimonolingual]`,
                      `r_Study[Berkes.et.al.2020,mobibilingual]`,
                      `r_Study[Ossher.et.al.2013,mobibilingual]`,
                      `r_Study[Ramakrishnan.et.al.2017,mobibilingual]`)


draws_long <- draws %>%
  pivot_longer(
    cols = starts_with("r_Study"),
    names_to = c("Study", "Group"),
    names_pattern = "r_Study\\[(.*),(.*)\\]"
  )

# Calculate study-specific effects and differences
draws_diff <- draws_long %>%
  pivot_wider(names_from = Group, values_from = value) %>%
  mutate(
    study_effect_mono = mobimonolingual + b_mobimonolingual,
    study_effect_bi = mobibilingual + b_mobibilingual,
    difference = study_effect_bi - study_effect_mono
  ) %>%
  select(Study, .draw, difference)

# Summarize the differences for each study
draws_summary <- draws_diff %>%
  group_by(Study) %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  ungroup()

# Add an summary effect row
overall_effect <- draws_diff %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  mutate(Study = "Summary_effect")

draws_summary <- bind_rows(draws_summary, overall_effect)

# Generate the forest plot
ggplot(draws_summary, aes(x = mean_diff, y = fct_reorder(Study, mean_diff))) +
  geom_vline(xintercept = 0, size = .25, lty = 2) +  # Vertical line at zero
  geom_pointrange(aes(xmin = lower, xmax = upper), size = .5) +  # Plot credible intervals
  geom_point(size = 3, color = "dodgerblue") +  # Plot mean differences
  geom_text(
    aes(label = glue("{round(mean_diff, 2)} [{round(lower, 2)}, {round(upper, 2)}]"), x = max(upper) + 0.5), 
    hjust = 0
  ) + 
  labs(
    title = "Forest Plot of Meta-analytic Effects in MCI sub-group",
    x = "Difference in Age at Onset",
    y = "Study"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) + 
  coord_cartesian(clip = "off", xlim = c(-4, 18))
```


```{r}
avg_comparisons(meta_analysismodel_5, variables = "mobi")
```


#Rerun the model after removing the studies that fall out of the funnel shape
```{r}
revised_retrospective <- read.csv("data/revised_retrospective.csv") %>% mutate(
    SE = SD / sqrt(N),
    mobi = factor(group, levels = c("monolingual", "bilingual"))
  )
```

```{r}
meta_analysismodel_6 <- brm(
  mean | se(SE) ~ 0 + mobi + (0 + mobi | Study),
  data = revised_retrospective,
  prior = meta_analysismodel_1_priors,
  cores = 4,
  file = "data/cache/meta_analysismodel_6",
  seed = seed
)
summary(meta_analysismodel_6)
```

```{r}
avg_comparisons(meta_analysismodel_6, variables = "mobi")
```



##read data
```{r}
prospective <- read_csv("data/prospective.csv") %>%
  mutate(
    mobi_2 = factor(group, levels = c("monolingual", "bilingual"))
  )
```

##fit model
```{r}
meta_analysismodel_7 <-brm(
  Dementia | trials(Total) ~ 0 + mobi_2 + (0 + mobi_2 | Study),
  data = prospective,
  family = binomial(),
  cores = 4,
  file = "data/cache/meta_analysismodel_7",
  seed = 1234
)
summary(meta_analysismodel_7)

```

```{r}
plot(meta_analysismodel_7, ask = FALSE)
```

#Drawing forest plot for incidence rates study
```{r}
model_draws <- spread_draws(meta_analysismodel_7, 
                      b_mobi_2monolingual, 
                      b_mobi_2bilingual, 
                      `r_Study[Lawton,.Gasquoine.&.Weimer,.2015,mobi_2monolingual]`, 
                      `r_Study[Ljungberg,.Hansson.&.Adolfsson,.2016,mobi_2monolingual]`,
                      `r_Study[Sanders.et.al.,.2012,mobi_2monolingual]`,
                      `r_Study[Venugopal.et.al.,.2023,mobi_2monolingual]`,
                      `r_Study[Yeung.et.al.,.2014,mobi_2monolingual]`,
                      `r_Study[Zahodne.et.al.,.2014,mobi_2monolingual]`,
                      `r_Study[Lawton,.Gasquoine.&.Weimer,.2015,mobi_2bilingual]`, 
                      `r_Study[Ljungberg,.Hansson.&.Adolfsson,.2016,mobi_2bilingual]`,
                      `r_Study[Sanders.et.al.,.2012,mobi_2bilingual]`,
                      `r_Study[Venugopal.et.al.,.2023,mobi_2bilingual]`,
                      `r_Study[Yeung.et.al.,.2014,mobi_2bilingual]`,
                      `r_Study[Zahodne.et.al.,.2014,mobi_2bilingual]`)

# Reshape data to long format for easier handling
draws_long <- model_draws %>%
  pivot_longer(
    cols = starts_with("r_Study"),
    names_to = c("Study", "Group"),
    names_pattern = "r_Study\\[(.*),(.*)\\]"
  )

# Calculate study-specific effects and differences
draws_diff <- draws_long %>%
  pivot_wider(names_from = Group, values_from = value) %>%
  mutate(
    study_effect_mono = `mobi_2monolingual` + b_mobi_2monolingual,
    study_effect_bi = `mobi_2bilingual` + b_mobi_2bilingual,
    difference = study_effect_bi - study_effect_mono
  ) %>%
  select(Study, .draw, difference)

# Summarize the differences for each study
draws_summary <- draws_diff %>%
  group_by(Study) %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  ungroup()

# Add an overall effect row
overall_effect <- draws_diff %>%
  summarise(
    mean_diff = mean(difference),
    lower = quantile(difference, 0.025),
    upper = quantile(difference, 0.975)
  ) %>%
  mutate(Study = "Summary_effect")

draws_summary <- bind_rows(draws_summary, overall_effect)

# Generate the forest plot
ggplot(draws_summary, aes(x = mean_diff, y = fct_reorder(Study, mean_diff))) +
  geom_vline(xintercept = 0, size = .25, lty = 2) +  # Vertical line at zero
  geom_pointrange(aes(xmin = lower, xmax = upper), size = .5) +  # Plot credible intervals
  geom_point(size = 3, color = "dodgerblue") +  # Plot mean differences
  geom_text(
    aes(label = glue("{round(mean_diff, 2)} [{round(lower, 2)}, {round(upper, 2)}]"), x = max(upper) + 0.5), 
    hjust = 0
  ) +  # Add text labels for each study
  labs(
    x = "Difference in Dementia Risk (log-odds)",
    y = "Study"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +  # Adjust text size if needed
  coord_cartesian(clip = "off", xlim = c(-2, 2))

```

```{r}
avg_comparisons(meta_analysismodel_7, variables = "mobi_2", comparison = "ratio")
```


```{r}
model_draws <- as_draws_df(meta_analysismodel_7)
names(model_draws)
```


#Rerun the model after removing Venugopal et al. (2023)

```{r}
Revised_prospective <- read_csv("data/Revised_prospective.csv") %>%
  mutate(
    mobi_2 = factor(group, levels = c("monolingual", "bilingual"))
  )

meta_analysismodel_8 <-brm(
  Dementia | trials(Total) ~ 0 + mobi_2 + (0 + mobi_2 | Study),
  data = Revised_prospective,
  family = binomial(),
  cores = 4,
  file = "data/cache/meta_analysismodel_8",
  seed = 1234
)
summary(meta_analysismodel_8)
```


```{r}
avg_comparisons(meta_analysismodel_8, variables = "mobi_2", comparison = "ratio")
```



